RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Proposal to move alpha

\subsection{Proposals that change the hyperparameters, keeping the objects fixed}

@@

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
%\section{``Galaxy Field'' Example}
%\section{``Transit'' example}

>>>>

\subsection{Proposals that change the hyperparameters, keeping the objects fixed}
Another kind of proposal that we will consider is a proposal that keeps all of
the objects fixed in place (i.e. leaves $\{x_i\}$) unchanged, but changes
the hyperparameter(s) from their current value $\alpha$
to a new value $\alpha'$. The proposal for the hyperparameter(s) is chosen
to satisfy detailed balance with respect to $p(\alpha)$.

The Metropolis acceptance probability must include the following factor:
\begin{eqnarray}
\frac{\prod_{i=1}^N p(x_i | \alpha')}{\prod_{i=1}^N p(x_i | \alpha)}
\end{eqnarray}

@@

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
%\section{``Galaxy Field'' Example}
